### 2025-08-09 draft.qmd
20250809 - clean up code

1) 9 total players of the following number at each of following positions:
- 1 Quarterback
- 2 Running Backs
- 2 Wide Receivers
- 1 Tight End
- 1 Flex: RB/WR/TE
- 1 K
- 1 DST

and 2) salary cap of \$200.

@@

# objective:
#f <- pts

# the variable are booleans
var.types <- rep("B", num.players)

# the constraints

A <- rbind(
  as.numeric(mostRecentProjections$pos == "QB"),                # num QB
  as.numeric(mostRecentProjections$pos == "RB"),                # num RB
  as.numeric(mostRecentProjections$pos == "WR"),                # num WR
  as.numeric(mostRecentProjections$pos == "TE"),                # num TE
  as.numeric(mostRecentProjections$pos == "K"),                 # num K
  as.numeric(mostRecentProjections$pos == "DST"),               # num DST
  as.numeric(mostRecentProjections$pos %in% c("RB","WR","TE")), # num flex
  total_players,
  mostRecentProjections$cost)                                   # player cost

>>>>

1. 9 total players of the following number at each of following positions:
    - 1 Quarterback
    - 2 Running Backs
    - 2 Wide Receivers
    - 1 Tight End
    - 1 Flex: RB/WR/TE
    - 1 K
    - 1 DST
1. salary cap of \$200.

@@

# the variables are booleans
var.types <- rep("B", num.players)

# the constraints
A <- rbind(
  as.numeric(mostRecentProjections$pos == "QB"),                # num QB
  as.numeric(mostRecentProjections$pos == "RB"),                # num RB
  as.numeric(mostRecentProjections$pos == "WR"),                # num WR
  as.numeric(mostRecentProjections$pos == "TE"),                # num TE
  as.numeric(mostRecentProjections$pos == "K"),                 # num K
  as.numeric(mostRecentProjections$pos == "DST"),               # num DST
  as.numeric(mostRecentProjections$pos %in% c("RB","WR","TE")), # num flex
  total_players,
  mostRecentProjections$cost)                                   # player cost
